network_analysis

### 2020-11-26 analyses/beta_diversity.Rmd
did so many things

# Permutation tests (slow)
gdm_WN.2010.imp <- gdm.varImp(sitepair_2010.WN, geo = TRUE, 
                              parallel = TRUE, cores = 2, # I think parallelization is a good idea (?)
                              sampleSitePairs = 0.5, # this randomly subsamples 50% of the site-pairs; a necessary sacrifice to get this to run smoothly, particularly for 2012
                              outFile = "./output/interaction_permGDM_2010") # save the output
gdm_WN.2011.imp <- gdm.varImp(sitepair_2011.WN, geo = TRUE, 
                              parallel = TRUE, cores = 2,
                              sampleSitePairs = 0.5,
                              outFile = "./output/interaction_permGDM_2011")
gdm_WN.2012.imp <- gdm.varImp(sitepair_2012.WN, geo = TRUE, 
                              parallel = TRUE, cores = 2,
                              sampleSitePairs = 0.5, # it keep crashing...
                              outFile = "./output/winteraction_permGDM_2012")

@@

## collate extracted splines  
interaction_splines <- bind_rows(interaction_splines2010, 
                                 interaction_splines2011, 
                                 interaction_splines2012) %>%
  mutate(x.var = case_when(
    x.var == "elev.mean" ~ "Elevation (m)",
    x.var == "Geographic" ~ "Geographic (km)",
    x.var == "yday" ~ "Day of Year")) %>%
  mutate(x.var = factor(x.var, levels = c("Geographic (km)", "Elevation (m)", "Day of Year")),
    subject = rep("BB*FL", dim(.)[1]))
```

@@

## collate extracted splines  
survey_splines <- bind_rows(survey_splines2010,
                            survey_splines2011, 
                            survey_splines2012) %>%
  mutate(x.var = case_when(
    x.var == "elev.mean" ~ "Elevation (m)",
    x.var == "Geographic" ~ "Geographic (km)",
    x.var == "yday" ~ "Day of Year"),
    x.var = factor(x.var, levels = c("Geographic (km)", "Elevation (m)", "Day of Year")),
    subject = rep("FL", n())
    )

@@

## collate extracted splines  
bb_splines <- bind_rows(bb_splines2010,
                            bb_splines2011, 
                            bb_splines2012) %>%
  mutate(x.var = case_when(
    x.var == "elev.mean" ~ "Elevation (m)",
    x.var == "Geographic" ~ "Geographic (km)",
    x.var == "yday" ~ "Day of Year"),
    x.var = factor(x.var, levels = c("Geographic (km)", "Elevation (m)", "Day of Year")),
    subject = rep("BB", n())
    )

@@

### Tabulate model output
```{r}
####### survey
gdm_survey.2010.tab1 <- gdm_survey.2010.imp[1] %>% 
  as.data.frame() %>%
  rownames_to_column() %>%
  as_tibble() %>%
  select(1, 2) %>%
  pivot_wider(names_from = rowname, values_from = 2) %>%
  mutate(subject = "survey",
         year = 2010) %>%
  select(subject, year, 
         mod.dev = `Model deviance`, 
         dev.exp = `Percent deviance explained`, 
         mod.pval = `Model p-value`)

@@

gdm_BB.tab_join <- bind_rows(gdm_BB.2010.tab_join,
                             gdm_BB.2011.tab_join,
                             gdm_BB.2012.tab_join) %>%
 # pivot_longer(cols = -c(subject, year), names_to = "var", values_to = "value") %>%
  gt() %>%
  tab_header(title = "GDM Model Output") %>%
  tab_spanner(
    label = "Model",
    columns = vars(mod.dev, dev.exp, mod.pval)
  ) %>%
  tab_spanner(
    label = "Variable importance",
    columns = vars(geo.imp, elev.imp, yday.imp)
  ) %>%
  tab_spanner(
    label = "Variable p-value",
    columns = vars(geo.pval, elev.pval, yday.pval)
  ) %>% 
  tab_row_group(
    group = "Bumble bee",
    rows = 1:3
  ) %>%
  fmt_number(
    columns = c("mod.dev", "dev.exp",
                "geo.imp", "elev.imp", "yday.imp"),
    decimals = 1
  )
```

@@

ggplot(splines, aes(predictor, response, color = subject)) +
  geom_line() +
  facet_grid(year ~ x.var, scales = "free_x") +
  xlab(NULL) +
  ylab("f(x)") +
  theme_light(12)
ggsave("./output/GDM.png", width = 6.5, height = 5, units = "in")
```
# If I could get this to work, it would be cool to transform and plot my GDMs. But the script crashes every time. 
```{r}

>>>>

# Permutation tests (slow)
gdm_WN.2010.imp <- gdm.varImp(sitepair_2010.WN, geo = TRUE, 
                              parallel = TRUE, cores = 2, # I think parallelization is a good idea (?)
                              sampleSitePairs = 0.5, # this randomly subsamples 50% of the site-pairs; a necessary sacrifice to get this to run smoothly, particularly for 2012
                              outFile = "./output/interaction_permGDM_2010") # save the output
gdm_WN.2011.imp <- gdm.varImp(sitepair_2011.WN, geo = TRUE, 
                              parallel = TRUE, cores = 2,
                              sampleSitePairs = 0.5,
                              outFile = "./output/interaction_permGDM_2011")
gdm_WN.2012.imp <- gdm.varImp(sitepair_2012.WN, geo = TRUE, 
                              parallel = TRUE, cores = 2,
                              sampleSitePairs = 0.5, # it keep crashing...
                              outFile = "./output/interaction_permGDM_2012")

@@

## collate extracted splines  
interaction_splines <- bind_rows(interaction_splines2010, 
                                 interaction_splines2011, 
                                 interaction_splines2012) %>%
  mutate(x.var = case_when(
    x.var == "elev.mean" ~ "Elevation",
    x.var == "Geographic" ~ "Geographic dist.",
    x.var == "yday" ~ "Time")) %>%
  mutate(x.var = factor(x.var, levels = c("Geographic dist.", "Elevation", "Time")),
    subject = rep("interaction", dim(.)[1]))
```

@@

## collate extracted splines  
survey_splines <- bind_rows(survey_splines2010,
                            survey_splines2011, 
                            survey_splines2012) %>%
  mutate(x.var = case_when(
    x.var == "elev.mean" ~ "Elevation",
    x.var == "Geographic" ~ "Geographic dist.",
    x.var == "yday" ~ "Time"),
    x.var = factor(x.var, levels = c("Geographic dist.", "Elevation", "Time")),
    subject = rep("FL", n())
    )

@@

## collate extracted splines  
bb_splines <- bind_rows(bb_splines2010,
                            bb_splines2011, 
                            bb_splines2012) %>%
  mutate(x.var = case_when(
    x.var == "elev.mean" ~ "Elevation",
    x.var == "Geographic" ~ "Geographic dist.",
    x.var == "yday" ~ "Time"),
    x.var = factor(x.var, levels = c("Geographic dist.", "Elevation", "Time")),
    subject = rep("BB", n())
    )

@@

### Tabulate model output
```{r}
# assign("gdm_WN.2010.imp", get(load("~/Documents/Research/bb_berchtesgaden/analyses/output/interaction_permGDM_2010.RData")))
# 
# assign("gdm_WN.2011.imp", get(load("~/Documents/Research/bb_berchtesgaden/analyses/output/interaction_permGDM_2011.RData")))
# 
# assign("gdm_WN.2012.imp", get(load("~/Documents/Research/bb_berchtesgaden/analyses/output/interaction_permGDM_2012.RData")))

####### WN
gdm_WN.2010.tab1 <- gdm_WN.2010.imp[1] %>% 
  as.data.frame() %>%
  rownames_to_column() %>%
  as_tibble() %>%
  select(1, 2) %>%
  pivot_wider(names_from = rowname, values_from = 2) %>%
  mutate(subject = "WN",
         year = 2010) %>%
  select(subject, year, 
         mod.dev = `Model deviance`, 
         dev.exp = `Percent deviance explained`, 
         mod.pval = `Model p-value`)

gdm_WN.2010.tab2 <- gdm_WN.2010.imp[2] %>% 
  as.data.frame() %>%
  rownames_to_column() %>%
  as_tibble() %>%
  select(1, 2) %>%
  pivot_wider(names_from = rowname, values_from = 2) %>%
  select(geo.imp = Geographic, elev.imp = elev.mean, yday.imp = yday)

gdm_WN.2010.tab3 <- gdm_WN.2010.imp[3] %>% 
  as.data.frame() %>%
  rownames_to_column() %>%
  as_tibble()  %>%
  select(1, 2) %>%
  pivot_wider(names_from = rowname, values_from = 2)  %>%
  select(geo.pval = Geographic, elev.pval = elev.mean, yday.pval = yday)

gdm_WN.2011.tab1 <- gdm_WN.2011.imp[1] %>% 
  as.data.frame() %>%
  rownames_to_column() %>%
  as_tibble() %>%
  select(1, 2) %>%
  pivot_wider(names_from = rowname, values_from = 2) %>%
  mutate(subject = "WN",
         year = 2011) %>%
  select(subject, year, 
         mod.dev = `Model deviance`, 
         dev.exp = `Percent deviance explained`, 
         mod.pval = `Model p-value`)

gdm_WN.2011.tab2 <- gdm_WN.2011.imp[2] %>% 
  as.data.frame() %>%
  rownames_to_column() %>%
  as_tibble() %>%
  select(1, 2) %>%
  pivot_wider(names_from = rowname, values_from = 2) %>%
  select(geo.imp = Geographic, elev.imp = elev.mean, yday.imp = yday)

gdm_WN.2011.tab3 <- gdm_WN.2011.imp[3] %>% 
  as.data.frame() %>%
  rownames_to_column() %>%
  as_tibble()  %>%
  select(1, 2) %>%
  pivot_wider(names_from = rowname, values_from = 2)  %>%
  select(geo.pval = Geographic, elev.pval = elev.mean, yday.pval = yday)

gdm_WN.2012.tab1 <- gdm_WN.2012.imp[1] %>% 
  as.data.frame() %>%
  rownames_to_column() %>%
  as_tibble() %>%
  select(1, 2) %>%
  pivot_wider(names_from = rowname, values_from = 2) %>%
  mutate(subject = "WN",
         year = 2012) %>%
  select(subject, year, 
         mod.dev = `Model deviance`, 
         dev.exp = `Percent deviance explained`, 
         mod.pval = `Model p-value`)

gdm_WN.2012.tab2 <- gdm_WN.2012.imp[2] %>% 
  as.data.frame() %>%
  rownames_to_column() %>%
  as_tibble() %>%
  select(1, 2) %>%
  pivot_wider(names_from = rowname, values_from = 2) %>%
  select(geo.imp = Geographic, elev.imp = elev.mean, yday.imp = yday)

gdm_WN.2012.tab3 <- gdm_WN.2012.imp[3] %>% 
  as.data.frame() %>%
  rownames_to_column() %>%
  as_tibble()  %>%
  select(1, 2) %>%
  pivot_wider(names_from = rowname, values_from = 2)  %>%
  select(geo.pval = Geographic, elev.pval = elev.mean, yday.pval = yday)

gdm_WN.2010.tab_join <- bind_cols(gdm_WN.2010.tab1,
                                  gdm_WN.2010.tab2, 
                                  gdm_WN.2010.tab3)

gdm_WN.2011.tab_join <- bind_cols(gdm_WN.2011.tab1,
                                  gdm_WN.2011.tab2, 
                                  gdm_WN.2011.tab3)

gdm_WN.2012.tab_join <- bind_cols(gdm_WN.2012.tab1,
                                  gdm_WN.2012.tab2, 
                                  gdm_WN.2012.tab3)

####### survey
gdm_survey.2010.tab1 <- gdm_survey.2010.imp[1] %>% 
  as.data.frame() %>%
  rownames_to_column() %>%
  as_tibble() %>%
  select(1, 2) %>%
  pivot_wider(names_from = rowname, values_from = 2) %>%
  mutate(subject = "survey",
         year = 2010) %>%
  select(subject, year, 
         mod.dev = `Model deviance`, 
         dev.exp = `Percent deviance explained`, 
         mod.pval = `Model p-value`)

@@

gdm_BB.tab_join <- bind_rows(gdm_BB.2010.tab_join,
                             gdm_BB.2011.tab_join,
                             gdm_BB.2012.tab_join,
                             gdm_survey.2010.tab_join,
                             gdm_survey.2011.tab_join,
                             gdm_survey.2012.tab_join,
                             gdm_WN.2010.tab_join,
                             gdm_WN.2011.tab_join,
                             gdm_WN.2012.tab_join) %>%
  select(-subject)

gdm_tab <- gdm_BB.tab_join %>%
  gt(rowname_col = "year") %>%
  tab_spanner(
    label = "Model",
    columns = vars(mod.dev, dev.exp, mod.pval)
  ) %>%
  tab_spanner(
    label = "Geographic distance",
    columns = vars(geo.imp, geo.pval)
  ) %>%
  tab_spanner(
    label = "Elevational distance",
    columns = vars(elev.imp, elev.pval)
  ) %>%
  tab_spanner(
    label = "Temporal distance",
    columns = vars(yday.imp, yday.pval)
  ) %>%
  tab_row_group(
    group = "Bumble bees",
    rows = 1:3
  ) %>% 
  tab_row_group(
    group = "Flora",
    rows = 4:6
  ) %>%
  tab_row_group(
    group = "Interactions",
    rows = 7:9
  ) %>%
  fmt_number(
    columns = c("mod.dev", "dev.exp",
                "geo.imp", "elev.imp", "yday.imp"),
    decimals = 1
  ) %>%
  fmt_number(
    columns = c("mod.pval", "geo.pval", 
                "elev.pval", "yday.pval"),
    decimals = 3
  ) %>%
  cols_label(mod.dev = "tot. dev.",
             dev.exp = "dev. expl. (%)",
             mod.pval = "p",
             geo.imp = "imp.",
             elev.imp = "imp.",
             yday.imp = "imp.",
             geo.pval = "p-val",
             elev.pval = "p-val",
             yday.pval = "p-val")

gdm_tab.nopval <- gdm_BB.tab_join %>%
  dplyr::select(-c(geo.pval, elev.pval, yday.pval, mod.pval)) %>%
  gt(rowname_col = "year") %>%
  tab_spanner(
    label = "Model",
    columns = vars(mod.dev, dev.exp)
  ) %>%
  tab_spanner(
    label = "Variable importance (%)",
    columns = vars(geo.imp, elev.imp, yday.imp)
  ) %>%
  tab_row_group(
    group = "Bumble bees",
    rows = 1:3
  ) %>% 
  tab_row_group(
    group = "Flora",
    rows = 4:6
  ) %>%
  tab_row_group(
    group = "Interactions",
    rows = 7:9
  ) %>%
  fmt_number(
    columns = c("mod.dev", "dev.exp",
                "geo.imp", "elev.imp", "yday.imp"),
    decimals = 1
  ) %>%
  cols_label(mod.dev = "tot. dev.",
             dev.exp = "dev. expl. (%)",
             geo.imp = "geo. dist.",
             elev.imp = "elev. dist.",
             yday.imp = "temp. dist.") %>%
  data_color(
    columns = vars(geo.imp, elev.imp, yday.imp),
    colors = scales::col_numeric(
      palette = c("white", "red"), 
      domain = c(-5, 100))
    ) %>%
  data_color(
    columns = vars(dev.exp),
    colors = scales::col_numeric(
      palette = c("white", "red"), 
      domain = c(-5, 100))
  )

gtsave(gdm_tab.nopval, "gdm_tab.png","./output/gdm_tab.png")

@@

# ggplot(splines, aes(predictor, response, color = subject)) +
#   geom_line() +
#   facet_grid(year ~ x.var, scales = "free_x") +
#   xlab(NULL) +
#   ylab("f(x)") +
#   theme_light(12)
# ggsave("./output/GDM.png", width = 6.5, height = 5, units = "in")

splot1 <- ggplot(filter(splines, x.var == "Geographic dist."), 
                 aes(predictor, response, color = subject)) +
  geom_line() +
  #facet_wrap(~year, ncol = 1, scales = "free_x") +
  facet_grid(year ~ x.var, scales = "free_x") +
  xlab("km") +
  ylab("f(x)") +
  ylim(c(0, 7)) +
  theme_light(12) +
  theme(legend.position = "none")

splot2 <- ggplot(filter(splines, x.var == "Elevation"), 
       aes(predictor, response, color = subject)) +
  geom_line() +
  #facet_wrap(~year, ncol = 1, scales = "free_x") +
  facet_grid(year ~ x.var, scales = "free_x") +
  xlab("m") +
  ylab(NULL) +
  ylim(c(0, 7)) +
  theme_light(12) +
  theme(legend.position = "none")

splot3 <- ggplot(filter(splines, x.var == "Time"), 
       aes(as_date(predictor), response, color = subject)) +
  geom_line() +
  #facet_wrap(~year, ncol = 1, scales = "free_x") +
  facet_grid(year ~ x.var, scales = "free_x") +
  xlab("date") +
  ylab(NULL) +
  ylim(c(0, 7)) +
  theme_light(12) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5))

png("./output/GDM_splines.png", width = 8, height = 5, units = "in", res = 300)
splot1 | splot2 | splot3
dev.off()
```

# If I could get this to work, it would be cool to transform and plot my GDMs. But the script crashes every time. 
```{r}

### 2020-11-26 analyses/old_scripts/BB_abund_GAM.Rmd
did so many things

### Tabulate plots
```{r}
bss2010 <- plot(sm(bb_abund.2010, 2)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. terrestris/lucorum")), x = NULL, y = NULL)
bss2011 <- plot(sm(bb_abund.2011, 2)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. terrestris/lucorum")), x = NULL, y = NULL)
bss2012 <- plot(sm(bb_abund.2012, 2)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. terrestris/lucorum")), x = NULL, y = NULL)

gers2010 <- plot(sm(bb_abund.2010, 3)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. gerstaeckeri")), x = NULL, y = NULL)
gers2011 <- ggplot() #too rare
gers2012 <- plot(sm(bb_abund.2012, 3)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. gerstaeckeri")), x = NULL, y = NULL)

hort2010 <- plot(sm(bb_abund.2010, 4)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. hortorum")), x = NULL, y = NULL)
hort2011 <- plot(sm(bb_abund.2011, 3)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. hortorum")), x = NULL, y = NULL)
hort2012 <- plot(sm(bb_abund.2012, 4)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. hortorum")), x = NULL, y = NULL)

hypn2010 <- plot(sm(bb_abund.2010, 5)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. hypnorum")), x = NULL, y = NULL)
hypn2011 <- plot(sm(bb_abund.2011, 4)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. hypnorum")), x = NULL, y = NULL)
hypn2012 <- ggplot()  #too rare

jone2010 <- plot(sm(bb_abund.2010, 6)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. jonellus")), x = NULL, y = NULL)
jone2011 <- plot(sm(bb_abund.2011, 5)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. jonellus")), x = NULL, y = NULL)
jone2012 <- plot(sm(bb_abund.2012, 5)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. jonellus")), x = NULL, y = NULL)

lapi2010 <- ggplot() # too rare 
lapi2011 <- plot(sm(bb_abund.2011, 6)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. lapidarius")), x = NULL, y = NULL)
lapi2012 <- plot(sm(bb_abund.2012, 6)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. lapidarius")), x = NULL, y = NULL)

mend2010 <- plot(sm(bb_abund.2010, 7)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. mendax")), x = NULL, y = NULL)
mend2011 <- plot(sm(bb_abund.2011, 7)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. mendax")), x = NULL, y = NULL)
mend2012 <- plot(sm(bb_abund.2012, 7)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. mendax")), x = NULL, y = NULL)

mont2010 <- plot(sm(bb_abund.2010, 8)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. monticola")), x = NULL, y = NULL)
mont2011 <- plot(sm(bb_abund.2011, 8)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE)+
  l_points() +
  labs(title = expression(italic("B. monticola")), x = NULL, y = NULL)
mont2012 <- plot(sm(bb_abund.2012, 8)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. monticola")), x = NULL, y = NULL)

muci2010 <- plot(sm(bb_abund.2010, 9)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. mucidis")), x = NULL, y = NULL)
muci2011 <- plot(sm(bb_abund.2011, 9)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. mucidis")), x = NULL, y = NULL)
muci2012 <- plot(sm(bb_abund.2012, 9)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. mucidis")), x = NULL, y = NULL)

pasc2010 <- plot(sm(bb_abund.2010, 10)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. pascuorum")), x = NULL, y = NULL)
pasc2011 <- plot(sm(bb_abund.2011, 10)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. pascuorum")), x = NULL, y = NULL)
pasc2012 <- plot(sm(bb_abund.2012, 10)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. pascuorum")), x = NULL, y = NULL)

prat2010 <- plot(sm(bb_abund.2010, 11)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. pratorum")), x = NULL, y = NULL)
prat2011 <- plot(sm(bb_abund.2011, 11)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. pratorum")), x = NULL, y = NULL)
prat2012 <- plot(sm(bb_abund.2012, 11)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. pratorum")), x = NULL, y = NULL)

psit2010 <- plot(sm(bb_abund.2010, 12)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. psithyrus")), x = NULL, y = NULL)
psit2011 <- plot(sm(bb_abund.2011, 12)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. psithyrus")), x = NULL, y = NULL)
psit2012 <- plot(sm(bb_abund.2012, 12)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. psithyrus")), x = NULL, y = NULL)

pyre2010 <- plot(sm(bb_abund.2010, 13)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. pyrenaeus")), x = NULL, y = NULL)
pyre2011 <- plot(sm(bb_abund.2011, 13)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. pyrenaeus")), x = NULL, y = NULL)
pyre2012 <- plot(sm(bb_abund.2012, 13)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. pyrenaeus")), x = NULL, y = NULL)

soro2010 <- plot(sm(bb_abund.2010, 14)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. soroensis")), x = NULL, y = NULL)
soro2011 <- plot(sm(bb_abund.2011, 14)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. soroensis")), x = NULL, y = NULL)
soro2012 <- plot(sm(bb_abund.2012, 14)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. soroensis")), x = NULL, y = NULL)

wurf2010 <- plot(sm(bb_abund.2010, 15)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. wurflenii")), x = NULL, y = NULL)
wurf2011 <- plot(sm(bb_abund.2011, 15)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  guides(fill = FALSE) +
  l_points() +
  labs(title = expression(italic("B. wurflenii")), x = NULL, y = NULL)
wurf2012 <- plot(sm(bb_abund.2012, 15)) +
  l_fitRaster() +
  l_fitContour(size = 0.1) +
  l_points() +
  guides(fill = FALSE) +
  labs(title = expression(italic("B. wurflenii")), x = NULL, y = NULL)

pdf("./output/BB_abund_major.pdf", height = 11, width = 8.5)
major_sp <- gridPrint(bss2010, bss2011, bss2012, 
                      pasc2010, pasc2011, pasc2012,
                      prat2010, prat2011, prat2012,
                      psit2010, psit2011, psit2012,
                      soro2010, soro2011, soro2012,
                      wurf2010, wurf2011, wurf2012, ncol = 3)
dev.off()

pdf("./output/BB_abund_highelev.pdf", height = 5.5, width = 8.5)
high_elev_sp <- gridPrint(pyre2010, pyre2011, pyre2012, 
                          mend2010, mend2011, mend2012,
                          mont2010, mont2011, mont2012, ncol = 3)
dev.off()

pdf("./output/BB_abund_minor.pdf", height = 11, width = 8.5)
minor_sp <- gridPrint(gers2010, gers2011, gers2012,
                      hort2010, hort2011, hort2012,
                      hypn2010, hypn2011, hypn2012,
                      jone2010, jone2011, jone2012,
                      lapi2010, lapi2011, lapi2012,
                      muci2010, muci2011, muci2012, ncol = 3)
dev.off()
```

>>>>

# Extract predictions
```{r}
# Function to build data set over which to generate predictions
newdata_build <- function(dat, y) {

  ## yday min/max
  min_yday <- min(filter(dat, year == y)$yday)
  max_yday <- max(filter(dat, year == y)$yday)

  ## elev min.max
  min_elev <- min(filter(dat, year == y)$elev.mean)
  max_elev <- max(filter(dat, year == y)$elev.mean)

  ## species list
  spp <- dat %>%
    filter(year == y & bb.total.abund >= 5) %>%
    select(bb.sp) %>%
    unique() %>%
    na.omit() ##### NEED TO FIGURE OUT WHERE THE NA COMES FROM!

  # sequence of 50 points along the yday and elev ranges, respectively
  seq_yday <- seq(min_yday, max_yday, length.out = 50)
  seq_elev <- seq(min_elev, max_elev, length.out = 50)

  newdata <- tibble(seq_yday, seq_elev) %>% # combine seqs into data frame
    complete(seq_yday, seq_elev) %>% # get all possible values
    crossing(spp) %>% # get all possible combos with species
    select(yday = seq_yday, elev.mean = seq_elev, bb.sp) # rename columns to match the original model inputs
}

newdata2010 <- newdata_build(bb_abund_sp, 2010)
newdata2011 <- newdata_build(bb_abund_sp, 2011)
newdata2012 <- newdata_build(bb_abund_sp, 2012)

# A little wrapper to make predictions and return a tibble with desired columns 
predict_func <- function(mod, new, y) {
  predict.bam(mod, newdata = new, type = "response") %>%
    data.frame() %>%
    tibble() %>%
    bind_cols(new) %>%
    select(yday, elev.mean, bb.sp, pred = 1) %>%
    mutate(year = rep(y, n()))
}

# Generate predictions
predict2010 <- predict_func(bb_abund.2010, newdata2010, 2010)
predict2011 <- predict_func(bb_abund.2011, newdata2011, 2011)
predict2012 <- predict_func(bb_abund.2012, newdata2012, 2012)
predict_pool <- bind_rows(predict2010, predict2011, predict2012)

# Subset predictions
predict_major <- filter(predict_pool, bb.sp %in% c("bss", "pasc", "prat", "soro", "wurf"))
predict_highelev <- filter(predict_pool, bb.sp %in% c("pyre", "mend", "mont"))
predict_minor <- filter(predict_pool, bb.sp %in% c("gers", "hort", "hypn","jone", "lapi", "muci"))

ggplot(predict_major, aes(yday, elev.mean, fill = log(pred))) +
  geom_raster() +
  geom_contour(aes(z = log(pred)), color = "black", size = 0.25) +
  scale_fill_viridis_c() +
  facet_grid(year~bb.sp)

ggplot(predict_highelev, aes(yday, elev.mean, fill = log(pred))) +
  geom_raster() +
  geom_contour(aes(z = log(pred)), color = "black", size = 0.25) +
  scale_fill_viridis_c() +
  facet_grid(year~bb.sp)

ggplot(predict_minor, aes(yday, elev.mean, fill = log(pred))) +
  geom_raster() +
  geom_contour(aes(z = log(pred)), color = "black", size = 0.25) +
  scale_fill_viridis_c() +
  facet_grid(year~bb.sp)
```

### 2020-11-26 analyses/old_scripts/network_analysis_bootstrapped.Rmd
did so many things

spmet_mean <- spmet %>%
  group_by(site, year) %>%
  #summarize(d = weighted.mean(d, bb.sp.abund, na.rm = TRUE)) %>%
  summarize(resource.range = weighted.mean(resource.range, bb.sp.abund, na.rm = TRUE)) %>%
  ungroup()

>>>>

spmet_mean <- spmet %>%
  group_by(site, year) %>%
  #summarize(d = weighted.mean(d, bb.sp.abund, na.rm = TRUE)) %>%
  summarize(resource.range = weighted.mean(resource.range, bb.sp.abund, na.rm = TRUE)) %>%
  #summarize(resource.range = mean(resource.range, na.rm = TRUE)) %>%
  ungroup()
